Data analysis to support temporary cycleways

### 2020-04-30 README.Rmd
Recentre Leeds and Bristol maps

roads_top = roads %>%
  filter(length > 300) %>%
  filter(name != "Broadway") %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)
tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = 13) + tm_scale_bar() +
  tm_basemap(server = s)

@@

tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = 13) + tm_scale_bar() +
  tm_basemap(server = s)

>>>>

roads_top = roads %>%
  filter(length > 300) %>%
  filter(name != "Broadway") %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)
tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = c(-1.549, 53.805, 13)) + 
  tm_scale_bar() +
  tm_basemap(server = s)

@@

tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = c(-2.5879, 51.454, 13)) + 
  tm_scale_bar() +
  tm_basemap(server = s)
